---
title: "Analyses"
format: html
editor: visual
---


# Phase 1
First selection chi square
```{r}
GoF(Data_phase_1$DV_1, Probs = c(0.5, 0.5))
```

Re-selection chi square
```{r}
GoF(Data_phase_1$DV_2, Probs = c(0.5, 0.5))
```

Selection beavior chi square
```{r}
GoF(Data_phase_1$changeDV[Data_phase_1$changeDV != 'change_To_Know'], Probs = c(1 / 3, 1 / 3, 1 / 3))
```

Who was more confidant?
```{r}
t_1 <- Data_phase_1 %>% 
  filter(conf_first == 'DK') %>% 
  mutate(confidance_identity = 'IDK') %>% 
  select(confidance = Confi_first, confidance_identity, Q1)
t_2 <- 
Data_phase_1 %>% 
  filter(conf_second == 'DK') %>% 
  mutate(confidance_identity = 'IDK') %>% 
  select(confidance = Confi_second, confidance_identity, Q1)
t_3 <- rbind(t_1, t_2)  


t_4 <- 
Data_phase_1 %>% 
  filter(conf_first == 'Know') %>% 
  mutate(confidance_identity = 'Know') %>% 
  select(confidance = Confi_first, confidance_identity, Q1)
t_5 <- 
Data_phase_1 %>% 
  filter(conf_second == 'Know') %>% 
  mutate(confidance_identity = 'Know') %>% 
  select(confidance = Confi_second, confidance_identity, Q1)
t_6 <- rbind(t_4, t_5)  

t_7 <- rbind(t_3, t_6)
t_7 %>% 
  arrange(Q1, confidance_identity)

pairedT(t_7$confidance, t_7$confidance_identity, Within = t_7$Q1)
```

Who was more accurate?
```{r}
t_1 <- Data_phase_1 %>% 
  filter(correctness_first == 'DK') %>% 
  mutate(confidance_identity = 'IDK') %>% 
  select(Accuracy = correct_first, confidance_identity, Q1)
t_2 <- 
Data_phase_1 %>% 
  filter(correctness_second == 'DK') %>% 
  mutate(confidance_identity = 'IDK') %>% 
  select(Accuracy = correct_second, confidance_identity, Q1)
t_3 <- rbind(t_1, t_2)  


t_4 <- 
Data_phase_1 %>% 
  filter(correctness_first == 'Know') %>% 
  mutate(confidance_identity = 'Know') %>% 
  select(Accuracy = correct_first, confidance_identity, Q1)
t_5 <- 
Data_phase_1 %>% 
  filter(correctness_second == 'Know') %>% 
  mutate(confidance_identity = 'Know') %>% 
  select(Accuracy = correct_second, confidance_identity, Q1)
t_6 <- rbind(t_4, t_5)  

t_7 <- rbind(t_3, t_6)


pairedT(t_7$Accuracy, t_7$confidance_identity, Within = t_7$Q1)
```

```{r}
Data_phase_1 %>% 
  select(METI_1_1, METI_1_2, METI_1_3, METI_1_4, METI_1_5, METI_1_6, METI_1_8, METI_2_1, METI_2_2, METI_2_3, METI_2_5, METI_2_6, METI_2_7, METI_2_8) %>% 
  alpha(cbind('METI_1_1', 'METI_1_2', 'METI_1_3', 'METI_1_4', 'METI_1_5', 'METI_1_6', 'METI_1_8', 'METI_2_1', 'METI_2_2', 'METI_2_3', 'METI_2_5', 'METI_2_6', 'METI_2_7', 'METI_2_8'))
Data_phase_1 %>% 
  select(METI_1_1, METI_1_2, METI_1_3, METI_1_4, METI_1_5, METI_1_6) %>% 
  alpha(cbind('METI_1_1', 'METI_1_2', 'METI_1_3', 'METI_1_4', 'METI_1_5', 'METI_1_6'))

Data_phase_1 %>% 
  select(METI_1_8, METI_2_1, METI_2_2, METI_2_3) %>% 
  alpha(cbind('METI_1_8', 'METI_2_1', 'METI_2_2', 'METI_2_3'))

Data_phase_1 %>% 
  select(METI_2_5, METI_2_6, METI_2_7, METI_2_8) %>% 
  alpha(cbind(
    'METI_2_5', 'METI_2_6', 'METI_2_7', 'METI_2_8'))


shapiro.test(Data_phase_1$METI)
shapiro.test(Data_phase_1$expertise)
shapiro.test(Data_phase_1$integrity)
shapiro.test(Data_phase_1$benevolence)

test_theoretical_dist(Data_phase_1$METI)
test_theoretical_dist(Data_phase_1$integrity)
test_theoretical_dist(Data_phase_1$benevolence)

chart.Correlation(Data_phase_1[, c('METI', 'expertise', 'integrity', 'benevolence')], histogram = TRUE, pch = 19)
```

## METI distribution
```{r}
oneSampleTest(Data_phase_1$METI, MU = 4, Parametric = TRUE)
```

## expertise distribution
```{r}
oneSampleTest(Data_phase_1$expertise, MU = 4, Parametric = TRUE)
```

## integrity distribution
```{r}
oneSampleTest(Data_phase_1$integrity, MU = 4, Parametric = TRUE)
```

## benevolence distribution
```{r}
oneSampleTest(Data_phase_1$benevolence, MU = 4, Parametric = TRUE)
```

## Behavior selection * METI
### METI
```{r}
oneWayAnova(Data_phase_1$METI[Data_phase_1$changeDV != 'change_To_Know'], Data_phase_1$changeDV[Data_phase_1$changeDV != 'change_To_Know'])
```

### expertise
```{r}
oneWayAnova(Data_phase_1$expertise[Data_phase_1$changeDV != 'change_To_Know'], Data_phase_1$changeDV[Data_phase_1$changeDV != 'change_To_Know'])
```

### integrity
```{r}
oneWayAnova(Data_phase_1$integrity[Data_phase_1$changeDV != 'change_To_Know'], Data_phase_1$changeDV[Data_phase_1$changeDV != 'change_To_Know'])
```

### benevolence
```{r}
oneWayAnova(Data_phase_1$benevolence[Data_phase_1$changeDV != 'change_To_Know'], Data_phase_1$changeDV[Data_phase_1$changeDV != 'change_To_Know'])
```


# Phase 2

```{r}
Data_phase_2 %>% 
  select(num_ITU1, num_ITU2, num_ITU3, num_ITU4, num_ITU5, num_ITU6
         , num_ITU7, num_ITU8, num_ITU9, num_ITU10, num_ITU11, num_ITU12) %>% 
  psych::alpha()

Data_phase_2 %>% 
  select(num_HH1, num_HH2, num_HH3, num_HH4, num_HH5
         , num_HH6, num_HH7, num_HH8, num_HH9, num_HH10) %>% 
  psych::alpha()

Data_phase_2 %>% 
  select(num_TA1, num_TA2, num_TA3, num_TA4, num_TA5, num_TA6
         , num_TA7, num_TA8, num_TA9, num_TA10, num_TA11, num_TA12) %>% 
  psych::alpha()

Data_phase_2 %>% 
  select(num_RWA1, num_RWA2, num_RWA3
         , num_RWA4, num_RWA5, num_RWA6) %>% 
  psych::alpha()

shapiro.test(Data_phase_2$norm_ITU_positive)
shapiro.test(Data_phase_2$norm_HH)
shapiro.test(Data_phase_2$norm_TA)
shapiro.test(Data_phase_2$norm_RWA_positive)

test_theoretical_dist(Data_phase_2$norm_RWA_positive)

chart.Correlation(Data_phase_2[, c('norm_ITU_positive', 'norm_HH', 'norm_TA', 'norm_RWA_positive')], histogram = TRUE, pch = 19, method = 'pearson')
```
## Questionnaires ~ First selection
### num_ITU_positive ~ selection 
```{r}
indttest(Data_phase_2$num_ITU_positive, Data_phase_2$DV_1)
```

### norm_HH ~ selection 
```{r}
indttest(Data_phase_2$norm_HH, Data_phase_2$DV_1)
```

### norm_TA ~ selection 
```{r}
indttest(Data_phase_2$norm_TA, Data_phase_2$DV_1)
```

### norm_RWA_positive ~ selection 
```{r}
indttest(Data_phase_2$norm_RWA_positive, Data_phase_2$DV_1)
```

### Logistic regression
```{r}
doSPSS::logReg(Data_phase_2$DV_1, Data_phase_2[, c('num_ITU_positive'
                                                   , 'norm_HH'
                                                   , 'norm_TA'
                                                   , 'norm_RWA_positive')])
```

## Questionnaires ~ changeDV
### num_ITU_positive ~ changeDV
```{r}
oneWayAnova(Data_phase_2$num_ITU_positive, Data_phase_2$changeDV)
```

### norm_HH ~ changeDV
```{r}
oneWayAnova(Data_phase_2$norm_HH, Data_phase_2$changeDV)
```

### norm_TA ~ changeDV
```{r}
oneWayAnova(Data_phase_2$norm_TA, Data_phase_2$changeDV)
```

### norm_RWA_positive ~ changeDV
```{r}
oneWayAnova(Data_phase_2$norm_RWA_positive, Data_phase_2$changeDV, Parametric = TRUE)
```


